
\newlist{keyskills}{itemize}{3}
\setlist[keyskills,1]{label=\textbullet,leftmargin=6mm}

\newcommand{\CVName}{Bastian Schmidt}
\newcommand{\CVWebsite}{\href{https://schmidt-systems.eu}{schmidt-systems.eu}}
\newcommand{\CVMail}{\href{mailto:basti@schmidt-electronics.de}{basti@schmidt-electronics.de}}
\newcommand{\CVGithub}{\href{https://github.com/bastian-src}{bastian-src}}
\newcommand{\CVPhone}{+49 151 12939370}
\newcommand{\CVAddress}{81541 Munich, Germany}
\newcommand{\CVBirthday}{November 11, 1997}
\newcommand{\CVNationality}{German}

\newcommand{\CVAboutMe}{
% Eager to learn new things, meet new people
Passionate about making things work and learning new tools.
Dives deep into nerdy topics of Linux, new programming languages and paradigms, software engineering and machine learning.
Strong focus on writing readable, testable, paralellizable and safe source code.
A terminal with Vim and tmux is all I need.
Likes hiking and poetry.}

% TODO: Edit this
\newcommand{\CVKeySkills}{
\begin{keyskills}
  \item \textbf{Artificial Intelligence}\\ ML, data vis, optimization
  \item \textbf{Robotics}\\ 7-DoF LWRs, Ontologies
  \item \textbf{CI \& Deployment}\\ Conan, Docker, Jenkins
  \item \textbf{Linux \& Terminal}\\ Fast with linux, vim, tmux
  \item \textbf{Languages}\\ C++, Python, Rust % TODO: fix C++ (use \verb)
\end{keyskills}
}

\newcommand{\CVLanguages}{
\begin{tabular}[c]{rl}
  \textbf{German} & Native \\
  \textbf{English} & C2 \\
  \textbf{Latin} & \\
\end{tabular}
}

\newcommand{\CVEducation}{
\CVEntry{2020 -- Now}{Technical University Munich (TUM)}{
    M.Sc.\ Computer Science\\
    Current grade: 1.7\\
}
\CVEntry{2021 -- 2022}{University of Utrecht (UU)}{
    2 Exchange Semester in the Netherlands\\
    Courses in Multimedia Retrieval, Game Physics, Sound and Music Technology\\
}
\CVEntry{2016 -- 2019}{Cooperative State University Mannheim (DHBW)}{
    B.Sc.\ Information and Communication Technology\\
    German Aerospace Center (DLR)\\
    Final grade: 1.7\\
}
\CVEntry{2013 -- 2016}{Johann-Conrad-Schlaun Berufskolleg (JCSBK)}{
    Allgemeine Hochschulreife\\
    Final grade: 1.2\\
}
}


% TODO: Edit this
\newcommand{\CVWork}{
\CVEntry{2020 -- Now}{Atix AG}{
    \textbf{Working Student.} Engineering team\\
    {
        %\small\begin{spacing}{0.9}
            Improving the \href{https://github.com/theforeman/foreman_salt}{Foreman Salt Plugin} and integrating Ubuntu Autoinstall into \href{https://theforeman.org/}{Foreman}.
        %\end{spacing}%
        \vspace{6mm}
    }
}
\CVEntry{2016 -- 2020}{German Aerospace Center (DLR)}{
    %Department of Cognitive Robotics, Industrial Robotics
}%
\CVSubEntry{2019 -- 2020}{
    \textbf{Research Scientist and Engineer.} Department of Communication Systems
    {
        \small\begin{spacing}{0.9}
        Part of the swarm exploration group.
        %Kinematic workspace analysis, autonomous task execution and ontological representation of data in the industrial robotics domain.
        \end{spacing}%
        \vspace{2pt}
    }%
}%
\CVSubEntry{2016 -- 2019}{
    \textbf{Working Student.} Department of Structural Dynamics and System Identification
    {
        \small\begin{spacing}{0.9}
        Part of the group for vibro-acoustic simulations and experiments.
        Joint dual study program with DHBW.
        \end{spacing}%
        \vspace{2pt}
    }
}
\vspace{5mm}
%\printbibliography[title=Publications]
}

% TODO: Edit this
\newcommand{\CVSkills}{
\begin{tcbraster}[raster columns=2]
    \begin{tcolorbox}[colback=white, boxrule=0pt, frame empty, nobeforeafter]
        {\color{textgray} Core Programming Languages }\\
        \Icon{\IconSize}{1.15}{./src/cpp.pdf}
        \Icon{\IconSize}{1.1}{./src/python.pdf}
        \Icon{\IconSize}{1.3}{./src/rust.pdf}
        \\\\
        {\color{textgray} Deployment Tools }\\
        \Icon{\IconSize}{1.1}{./src/cmake.pdf}
        \Icon{\IconSize}{1.1}{./src/conan.pdf}
        \Icon{\IconSize}{1.3}{./src/docker.pdf}
        \Icon{\IconSize}{1.05}{./src/jenkins.pdf}
        \Icon{\IconSize}{1.1}{./src/artifactory.pdf}
        \\\\
        {\color{textgray} Other Tools }\\
        \Icon{\IconSize}{1.0}{./src/neovim.pdf}
        \hspace*{-6pt}
        \Icon{\IconSize}{1.25}{./src/github.pdf}
        \Icon{\IconSize}{1.1}{./src/javascript.pdf}
        \Icon{\IconSize}{1.1}{./src/webassembly.pdf}
        \begin{minipage}[c]{\IconSize\textwidth}
            \vspace*{4pt}
            \hspace*{-3.5pt}
            \LARGE \LaTeX
        \end{minipage}
    \end{tcolorbox}
\end{tcbraster}
}


